IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/jcm.tex
file for jcm

@@

\title{
Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control
}
%   Generic, Efficient, Coarse-grained Information Flow Control
%   IFC For Me
%   Who knew adding IFC could be us easy?
%   Language-polymorphic schemes of dynamic information flow control
%   Target language and IFC language: shake to mix
%   1. Target language, 2. IFC language, 3. ... 4. Profit!!!
%   Just add IFC

@@

\maketitle

\input{abstract}
\input{intro}

@@

Our overall plan will be to take a \textbf{{\color{red} target language}} with a formal
operational semantics and combine it with an \textit{{\color{blue} information
flow control language}}.  For concreteness, we use a simple, untyped,
ML-like language with mutable references as our target language.
However, our technique will be indifferent to the actual target language
chosen: it need only be prepared for interoperability by being expressed
in the style of Matthews and
Findler~\cite{Matthews:2007:OSM:1190216.1190220}.  This procedure will
equip the target language with primitives for implementing dynamic
information control in the style of LIO~\cite{lio}, which we will
describe in more detail shortly.

We have typeset nonterminals of the target language using \textbf{{\color{red}
bold font}} while the nonterminals of the IFC language have been typeset
with \textit{{\color{blue} italic font}}.  Readers are encouraged to view
a color copy of this paper, where target language nonterminals are colored red
while IFC language nonterminals are colored blue.

\subsection{Target language: Mini-ML}

In Figure~\ref{fig:ml}, we give a simple, untyped ML-like language with
mutable references and errors, prepared for combination with an
information flow control language.  The presentation is standard, but it
is worth paying some attention to the Felleisen-Hieb reduction
semantics~\cite{Felleisen:1992:RRS:136293.136297} used to define the
operational semantics of the system.  Our language defines an evaluation
context \ensuremath{\tar{E}}; however, the evaluation rules have been expressed in terms
of a different evaluation context $\mathcal{E}_{\tar{\Sigma}}$.  To
derive the usual operational semantics for this language, the evaluation
context merely needs to be defined as \ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\tar{e}\right]\triangleq{}\tar{\Sigma},\tar{E}\;[\mskip1.5mu \tar{e}\mskip1.5mu]}.
However, when we combine this language with an IFC language, we must
reinterpret the meaning of this evaluation context.
In general, we require that a target language be expressed in terms
of some global machine state \ensuremath{\tar{\Sigma}}, some evaluation context \ensuremath{\tar{E}},
some expressions \ensuremath{\tar{e}}, some set of values \ensuremath{\tar{v}} and a reduction
relations on full configurations $\ensuremath{\tar{\Sigma}} \times \ensuremath{\tar{E}} \times \ensuremath{\tar{e}}$.

\begin{figure}
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{6}{@{}>{\hspre}l<{\hspost}@{}}%
\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
\column{22}{@{}>{\hspre}l<{\hspost}@{}}%
\column{40}{@{}>{\hspre}l<{\hspost}@{}}%
\column{47}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\tar{v}{}\<[6]%
\>[6]{}\Coloneqq\lambda \tar{x}.\tar{e}\mid \mathbf{true}\mid \mathbf{false}\mid \tar{a}{}\<[E]%
\\
\>[B]{}\tar{e}{}\<[6]%
\>[6]{}\Coloneqq\tar{v}\mid \tar{x}\mid \tar{e}\;\tar{e}\mid \mathbf{if}\;\tar{e}\;\mathbf{then}\;\tar{e}\;\mathbf{else}\;\tar{e}\mid \mathbf{ref}\;\tar{e}\mid \mathbin{!}\tar{e}\mid \tar{e}\mathbin{:=}\tar{e}{}\<[E]%
\\
\>[B]{}\tar{E}{}\<[6]%
\>[6]{}\Coloneqq\tar{[\cdot ]_T}\mid \tar{E}\;\tar{e}\mid \tar{v}\;\tar{E}\mid \mathbf{if}\;\tar{E}\;\mathbf{then}\;\tar{e}\;\mathbf{else}\;\tar{e}{}\<[E]%
\\
\>[6]{}\hsindent{2}{}\<[8]%
\>[8]{}\mid \mathbf{ref}\;\tar{E}\mid \mathbin{!}\tar{E}\mid \tar{E}\mathbin{:=}\tar{e}\mid \tar{v}\mathbin{:=}\tar{E}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\tar{e}_{1};\tar{e}_{2}{}\<[22]%
\>[22]{}\triangleq{}(\lambda \tar{x}.\tar{e}_{2})\;\tar{e}_{1}\;{}\<[40]%
\>[40]{}\mathbf{where}\;{}\<[47]%
\>[47]{}\tar{x}\;\not\in\;\mathcal{FV}\;(\tar{e}_{2}){}\<[E]%
\\
\>[B]{}\mathbf{let}\;\tar{x}\mathrel{=}\tar{e}_{1}\;\mathbf{in}\;\tar{e}_{2}{}\<[22]%
\>[22]{}\triangleq{}(\lambda \tar{x}.\tar{e}_{2})\;\tar{e}_{1}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

@@

\and
\inferrule[T-app]
{ } {\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[(\lambda \Varid{x}.\tar{e})\;\tar{v}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\{\mskip1.5mu \tar{v}\mathbin{/}\Varid{x}\mskip1.5mu\}\;\tar{e}\right]}}

@@

\and
\inferrule[T-deref]
{ \ensuremath{(\tar{a},\tar{v})\;\mathbf{in}\;\tar{\Sigma}} }
{\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\mathbin{!}\tar{a}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\tar{v}\right]}}

@@

@@

\caption{Simple ML-like language \ensuremath{\Red{\lambda_{\text{ML}}}}}
\label{fig:ml}
\end{figure}

@@

Information flow control seeks to enforce a security policy known as
\emph{non-interference}: public results must not depend on secret inputs.
Modern, dynamic IFC systems usually achieve this by associating a \emph{label}
with data, which encodes a policy of whether or not data tagged with one
label can flow to another label (written as \ensuremath{\flows}).
Since our embedding is agnostic
to the choice of labeling scheme, we simply represent labels with the metavariable
$l$, but do not discuss them in more detail.

In Figure~\ref{fig:ifc}, we give the syntax and \emph{single-threaded}
evaluation rules for a minimal information-flow control language.  The
evaluation context $\mathcal{E}_{\ifc{\Sigma}}$ represents the context
of the current task which is running, including on the right-hand side
the current label $l$ (which protects the program counter of the task)
and the task ID $i$.

Ordinarily, information flow control languages are defined by directly
stating a base language plus information flow control operators.  In
contrast, our language is purposely minimal: it does not have sequencing
operations, control flow, or other constructs.  However, it contains
support for the following core information flow control features:

\begin{itemize}
    \item First-class labels, with label values $l$ as well as operations for computing on
labels (\ensuremath{\flows}, \ensuremath{\lub} and \ensuremath{\glb}),
    \item operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (a task can only increase its label, and not decrease it),
    \item operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
        which interact with the global store of per-task message queues \ensuremath{\ifc{\Sigma}}, and
    \item a sandboxing operation allowing to spawn new
    isolated tasks, which will be described in more detail in the
    next section.
\end{itemize}

The form of \textbf{send}/\textbf{recv} are \Red{inspired by methods of inter-worker communication
in web browser APIs} \Red{cite}, however in Section~\ref{sec:extensions} we
discuss other possible choices for information flow control aware communication
primitives.  Their rules are different from non-IFC systems
and worth commenting on: when a task places
a message on the message queue of receiving task, it also labels that
message with a label \ensuremath{\ifc{\Varid{l}}'} (which must be above the tasks current label \ensuremath{\ifc{\Varid{l}}})
When the recipient reads out messages from its queue,
messages whose labels do not
flow to \ensuremath{\ifc{\Varid{l}}} are filtered out (denoted by \ensuremath{\ifc{\Theta}\preceq\ifc{\Varid{l}}}).
Specifically, if \ensuremath{\ifc{\Theta}} is the empty list \ensuremath{\epsilon}, the
function is simply the identity function, i.e.,
\ensuremath{\epsilon\preceq\ifc{\Varid{l}}\mathrel{=}\epsilon}; otherwise:
\[
\ensuremath{(\ifc{\Varid{l}}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\preceq\ifc{\Varid{l}}} = \left\{
\begin{array}{l l}
\ensuremath{(\ifc{\Varid{l}}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\preceq\ifc{\Varid{l}}} & \quad \text{if \ensuremath{\ifc{\Varid{l}}'\;\flows\;\ifc{\Varid{l}}}}\\
\ensuremath{\ifc{\Theta}\preceq\ifc{\Varid{l}}} & \quad \text{otherwise}
\end{array} \right.
\]
This ensures that tasks cannot receive messages that are more secret
than their current label would allow.

%   \begin{figure}
%   Typing judgment: $|tyrule tG tS te tty|$
%   \begin{mathpar}
%   \inferrule[T-ty-address]
%   {}
%   {| tyrule tG tS a (ref (tyLookup tS a)) |}
%   \end{mathpar}

%   \caption{Selected typing rules for ML-like language}
%   \label{fig:ml-typing}
%   \end{figure}

\begin{figure}
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{6}{@{}>{\hspre}c<{\hspost}@{}}%
\column{6E}{@{}l@{}}%
\column{8}{@{}>{\hspre}c<{\hspost}@{}}%
\column{8E}{@{}l@{}}%
\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\otimes{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\flows\mid \lub\mid \glb{}\<[E]%
\\
\>[B]{}\ifc{\Varid{v}}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\ifc{\Varid{i}}\mid \ifc{\Varid{l}}\mid \mathbf{true}\mid \mathbf{false}\mid \langle\rangle{}\<[E]%
\\
\>[B]{}\ifc{\Varid{e}}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\ifc{\Varid{v}}\mid \ifc{\Varid{x}}\mid \ifc{\Varid{e}}\;\otimes\;\ifc{\Varid{e}}\mid \mathbf{getLabel}\mid \mathbf{setLabel}\;\ifc{\Varid{e}}{}\<[E]%
\\
\>[6]{}\hsindent{2}{}\<[8]%
\>[8]{}\mid {}\<[8E]%
\>[11]{}\mathbf{sandbox}\;\ifc{\Varid{e}}\mid \mathbf{send}\;\ifc{\Varid{e}}\;\ifc{\Varid{e}}\;\ifc{\Varid{e}}\mid \ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}.\ifc{\Varid{e}}\;\ifc{\Varid{e}}{}\<[E]%
\\
\>[B]{}\ifc{E}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\ifc{[\cdot ]_I}\mid \ifc{E}\;\otimes\;\ifc{\Varid{e}}\mid \ifc{\Varid{v}}\;\otimes\;\ifc{E}\mid \mathbf{setLabel}\;\ifc{E}\mid \mathbf{sandbox}\;\ifc{E}{}\<[E]%
\\
\>[6]{}\hsindent{2}{}\<[8]%
\>[8]{}\mid {}\<[8E]%
\>[11]{}\mathbf{send}\;\ifc{E}\;\ifc{\Varid{e}}\;\ifc{\Varid{e}}\mid \mathbf{send}\;\ifc{\Varid{v}}\;\ifc{E}\;\ifc{\Varid{e}}\mid \mathbf{send}\;\ifc{\Varid{v}}\;\ifc{\Varid{v}}\;\ifc{E}{}\<[E]%
\\
\>[6]{}\hsindent{2}{}\<[8]%
\>[8]{}\mid {}\<[8E]%
\>[11]{}\ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\Leftarrow\mathbf{recv}.\ifc{\Varid{e}}\;\ifc{\Varid{e}}{}\<[E]%
\\
\>[B]{}\ifc{\theta}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}(\ifc{\Varid{l}},\ifc{\Varid{i}}\;\ifc{\Varid{e}}){}\<[E]%
\\
\>[B]{}\ifc{\Theta}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\epsilon\mid \ifc{\theta},\ifc{\Theta}{}\<[E]%
\\
\>[B]{}\ifc{\Sigma}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\emptyset\mid \ifc{\Sigma}\left[\ifc{\Varid{i}}\mapsto{}\ifc{\Theta}\right]{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

@@

\and
\inferrule[I-getLabel]
{ }
{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\mathbf{getLabel}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}}\left[\ifc{\Varid{l}}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}}

\and
\inferrule[I-setLabel]
{ \ensuremath{\ifc{\Varid{l}}\;\flows\;\ifc{\Varid{l}}'} }
{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\mathbf{setLabel}\;\ifc{\Varid{l}}'\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}}\left[\langle\rangle\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}'}}}
%{|fresh (id')|}

\and
\inferrule[I-send]
{
\ensuremath{\ifc{\Varid{l}}\;\flows\;\ifc{\Varid{l}}'}\\
\ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}}')\mathrel{=}\ifc{\Theta}}\\
\ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}'\mapsto{}(\ifc{\Varid{l}}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\right]}
}
{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}\left[\mathbf{send}\;\ifc{\Varid{i}}'\;\ifc{\Varid{l}}'\;\ifc{\Varid{e}}\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}\rightarrow\mathcal{E}_{\ifc{\Sigma}'}\left[\langle\rangle\right]^{\ifc{\Varid{i}}}_{\ifc{\Varid{l}}}}}

>>>>

\usepackage{url}

@@

\title{
IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control
}
%   Generic, Efficient, Coarse-grained Information Flow Control
%   IFC For Me
%   Who knew adding IFC could be us easy?
%   Language-polymorphic schemes of dynamic information flow control
%   Target language and IFC language: shake to mix
%   1. Target language, 2. IFC language, 3. ... 4. Profit!!!
%   Just add IFC

@@

\maketitle
\input{abstract}
\input{intro}

@@

Our overall plan will be to take a \textbf{{\color{red} target
language}} with a formal operational semantics and combine it with an
\textit{{\color{blue} information flow control language}}.  For example,
taking ECMAScript as the target language and combining it with our IFC
language should produce the formal semantics for SWAPI.  In this
presentation, we use a simple, untyped lambda calculus with mutable
references and fixpoint in place of ECMAScript, to demonstrate some of the key
properties without having too much detail; we discuss the proper
embedding in more detail in Section~\ref{sec:real}.

We have typeset nonterminals of the target language using \textbf{{\color{red}
bold font}} while the nonterminals of the IFC language have been typeset
with \textit{{\color{blue} italic font}}.  Readers are encouraged to view
a color copy of this paper, where target language nonterminals are colored \textbf{{\color{red} red}}
while IFC language nonterminals are colored \textit{{\color{blue} blue}}.

\subsection{Target language: Mini-ES}

In Figure~\ref{fig:ml}, we give a simple, untyped lambda calculus with
mutable references and fixpoint, prepared for combination with an
information flow control language.  The presentation is standard, and utilizes Felleisen-Hieb reduction
semantics~\cite{Felleisen:1992:RRS:136293.136297} to define the
operational semantics of the system.  Our language defines an evaluation
context \ensuremath{\tar{E}}; however, the evaluation rules have been expressed in terms
of a different evaluation context \ensuremath{\mathcal{E}_{\tar{\Sigma}}},
following the approach of Matthews and
Findler~\cite{Matthews:2007:OSM:1190216.1190220} to combine operational
semantics of multiple languages.  To
derive the usual operational semantics for this language, the evaluation
context merely needs to be defined as \ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\tar{e}\right]\triangleq{}\tar{\Sigma},\tar{E}\left[\tar{e}\right]}.
However, when we combine this language with an IFC language, we must
reinterpret the meaning of this evaluation context.
In general, we require that a target language be expressed in terms
of some global machine state \ensuremath{\tar{\Sigma}}, some evaluation context \ensuremath{\tar{E}},
some expressions \ensuremath{\tar{e}}, some set of values \ensuremath{\tar{v}} and a \emph{deterministic}
reduction relation on full configurations $\ensuremath{\tar{\Sigma}} \times \ensuremath{\tar{E}} \times \ensuremath{\tar{e}}$.

\begin{figure}
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{6}{@{}>{\hspre}l<{\hspost}@{}}%
\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
\column{22}{@{}>{\hspre}l<{\hspost}@{}}%
\column{40}{@{}>{\hspre}l<{\hspost}@{}}%
\column{47}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\tar{v}{}\<[6]%
\>[6]{}\Coloneqq\lambda \tar{x}.\tar{e}\mid \mathbf{true}\mid \mathbf{false}\mid \tar{a}{}\<[E]%
\\
\>[B]{}\tar{e}{}\<[6]%
\>[6]{}\Coloneqq\tar{v}\mid \tar{x}\mid \tar{e}\;\tar{e}\mid \mathbf{if}\;\tar{e}\;\mathbf{then}\;\tar{e}\;\mathbf{else}\;\tar{e}{}\<[E]%
\\
\>[6]{}\hsindent{2}{}\<[8]%
\>[8]{}\mid \mathbf{ref}\;\tar{e}\mid \mathbin{!}\tar{e}\mid \tar{e}\mathbin{:=}\tar{e}\mid \mathbf{fix}\;\Varid{e}{}\<[E]%
\\
\>[B]{}\tar{E}{}\<[6]%
\>[6]{}\Coloneqq\tar{[\cdot ]_T}\mid \tar{E}\;\tar{e}\mid \tar{v}\;\tar{E}\mid \mathbf{if}\;\tar{E}\;\mathbf{then}\;\tar{e}\;\mathbf{else}\;\tar{e}{}\<[E]%
\\
\>[6]{}\hsindent{2}{}\<[8]%
\>[8]{}\mid \mathbf{ref}\;\tar{E}\mid \mathbin{!}\tar{E}\mid \tar{E}\mathbin{:=}\tar{e}\mid \tar{v}\mathbin{:=}\tar{E}\mid \mathbf{fix}\;E{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\tar{e}_{1};\tar{e}_{2}{}\<[22]%
\>[22]{}\triangleq{}(\lambda \tar{x}.\tar{e}_{2})\;\tar{e}_{1}\;{}\<[40]%
\>[40]{}\mathbf{where}\;{}\<[47]%
\>[47]{}\tar{x}\;\not\in\;\mathcal{FV}\;(\tar{e}_{2}){}\<[E]%
\\
\>[B]{}\mathbf{let}\;\tar{x}\mathrel{=}\tar{e}_{1}\;\mathbf{in}\;\tar{e}_{2}{}\<[22]%
\>[22]{}\triangleq{}(\lambda \tar{x}.\tar{e}_{2})\;\tar{e}_{1}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

@@

\inferrule[T-app]
{ } {\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[(\lambda \Varid{x}.\tar{e})\;\tar{v}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\{\mskip1.5mu \tar{v}\mathbin{/}\Varid{x}\mskip1.5mu\}\;\tar{e}\right]}}

@@

\and
\inferrule[T-deref]
{ \ensuremath{(\tar{a},\tar{v})\in\tar{\Sigma}} }
{\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\mathbin{!}\tar{a}\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\tar{v}\right]}}

@@

\and
\inferrule[T-fix]
{ }
{\ensuremath{\mathcal{E}_{\tar{\Sigma}}\left[\mathbf{fix}\;(\lambda \Varid{x}.\Varid{e})\right]\rightarrow\mathcal{E}_{\tar{\Sigma}}\left[\{\mskip1.5mu \mathbf{fix}\;(\lambda \Varid{x}.\Varid{e})\mathbin{/}\Varid{x}\mskip1.5mu\}\;\Varid{e}\right]}}

@@

\caption{Simple untyped lambda calculus \ensuremath{\Red{\lambda_{\text{ES}}}}}
\label{fig:ml}
\end{figure}

@@

Most modern, dynamic information flow control languages encode
policy by associating a \emph{label}
with data, which encodes whether or not data tagged with one
label \ensuremath{l_{1}} can flow to another label \ensuremath{l_{2}} (written as \ensuremath{l_{1}\flows{}l_{2}}).
Our embedding is agnostic to the choice of labeling scheme; we only
require the labels to form a lattice~\cite{Denning:1976:LMS:360051.360056}
with the partial order \ensuremath{\flows{}}.
In this paper, we simply represent labels with the metavariable
$l$, but do not discuss them in more detail.

In Figure~\ref{fig:ifc}, we give the syntax and \emph{single-threaded}
evaluation rules for a minimal information-flow control language.  
Ordinarily, information flow control languages are defined by directly
stating a base language plus information flow control operators.  In
contrast, our language is purposely minimal: it does not have sequencing
operations, control flow, or other constructs.  However, it contains
support for the following core information flow control features:

\begin{itemize}
    \item First-class labels, with label values $l$ as well as operations for computing on
labels (\ensuremath{\flows{}}, \ensuremath{\lub} and \ensuremath{\glb}),
    \item Operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (a task can only increase its label, and not decrease it),
    \item Operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
        which interact with the global store of per-task message queues \ensuremath{\ifc{\Sigma}}, and
    \item A sandboxing operation allowing to spawn new
    isolated tasks, which will be described in more detail in the
    next section.
\end{itemize}

While the first two bullet points are essentially universal to all
floating-label systems, our choice of communication primitives is motivated
by inter-worker communication in web browser APIs~\cite{webworkers}, but
other choices such as blocking communication or labeled channels are possible.
We describe some of the alternate possibilities in Section~\ref{sec:extensions}.
These operations are all defined with respect to an evaluation context \ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}} represents the context
of the current task which is running, which has three important pieces
of state: the global message queues \ensuremath{\ifc{\Sigma}},
the current label \ensuremath{\ifc{l}} (which protects the program counter of the task)
and the task ID \ensuremath{\ifc{\Varid{i}}}.

Our asynchronous communication primitives are worth some further
discussion.  When a task is sending a message using \ensuremath{\mathbf{send}}, it also labels that
message with a label \ensuremath{\ifc{l}'} (which must be above the tasks current label \ensuremath{\ifc{l}}).
Messages can only be received by a task if its current label is
at least as high as the label of the message.
Specifically, receiving a message using
\[ \ensuremath{\mathbf{recv}\ \ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\;\mathbf{in}\;\ifc{\Varid{e}}_{1}\ \mathbf{else}\ \ifc{\Varid{e}}_{2}} \]
binds the message and the senders task identifier
to local variables \ensuremath{\ifc{\Varid{x}}_{1}} and \ensuremath{\ifc{\Varid{x}}_{2}}, respectively, and then executes \ensuremath{\ifc{\Varid{e}}_{1}}.
Otherwise the message gets removed from the queue by rule \textsc{I-noRecv},
and that tasks continues its execution with \ensuremath{\ifc{\Varid{e}}_{2}}.
We denote the filtering of the message queue by \ensuremath{\ifc{\Theta}\preceq\ifc{l}},
which is defined as follows.
If \ensuremath{\ifc{\Theta}} is the empty list \ensuremath{\epsilon}, the
function is simply the identity function, i.e.,
\ensuremath{\epsilon\preceq\ifc{l}\mathrel{=}\epsilon}; otherwise:
\[
\ensuremath{(\ifc{l}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\preceq\ifc{l}} = \left\{
\begin{array}{l l}
\ensuremath{(\ifc{l}',\ifc{\Varid{i}},\ifc{\Varid{e}}),\ifc{\Theta}\preceq\ifc{l}} & \quad \text{if \ensuremath{\ifc{l}'\;\flows{}\;\ifc{l}}}\\
\ensuremath{\ifc{\Theta}\preceq\ifc{l}} & \quad \text{otherwise}
\end{array} \right.
\]
This ensures that tasks cannot receive messages that are more secret
than their current label would allow.

As a final remark, blocking receive can be (inefficiently) implemented using
our asynchronous primitives as follows:
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[3]{}\mathbf{blockingRecv}\ \ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\;\mathbf{in}\;\ifc{\Varid{e}}\triangleq{}{}\<[E]%
\\
\>[3]{}\ \ \;\ \ \;\ \ \;\ifc{^{\textrm{IT}}\lceil}\mathbf{fix}\;(\lambda \Varid{k}.\tar{_{\textrm{TI}}\lfloor}\mathbf{recv}\ \ifc{\Varid{x}}_{1},\ifc{\Varid{x}}_{2}\;\mathbf{in}\;\ifc{\Varid{e}}\ \mathbf{else}\ \ifc{^{\textrm{IT}}\lceil}\Varid{k}\ifc{\rceil}\tar{\rfloor})\ifc{\rceil}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\begin{figure}
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{6}{@{}>{\hspre}c<{\hspost}@{}}%
\column{6E}{@{}l@{}}%
\column{8}{@{}>{\hspre}c<{\hspost}@{}}%
\column{8E}{@{}l@{}}%
\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\otimes{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\flows{}\mid \lub\mid \glb{}\<[E]%
\\
\>[B]{}\ifc{\Varid{v}}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\ifc{\Varid{i}}\mid \ifc{l}\mid \mathbf{true}\mid \mathbf{false}\mid \langle\rangle{}\<[E]%
\\
\>[B]{}\ifc{\Varid{e}}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\ifc{\Varid{v}}\mid \ifc{\Varid{x}}\mid \ifc{\Varid{e}}\;\otimes\;\ifc{\Varid{e}}\mid \mathbf{getLabel}\mid \mathbf{setLabel}\;\ifc{\Varid{e}}\mid \mathbf{taskId}{}\<[E]%
\\
\>[6]{}\hsindent{2}{}\<[8]%
\>[8]{}\mid {}\<[8E]%
\>[11]{}\mathbf{sandbox}\;\ifc{\Varid{e}}\mid \mathbf{send}\;\ifc{\Varid{e}}\;\ifc{\Varid{e}}\;\ifc{\Varid{e}}\mid \mathbf{recv}\ \ifc{\Varid{x}},\ifc{\Varid{x}}\;\mathbf{in}\;\ifc{\Varid{e}}\ \mathbf{else}\ \ifc{\Varid{e}}{}\<[E]%
\\
\>[B]{}\ifc{E}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\ifc{[\cdot ]_I}\mid \ifc{E}\;\otimes\;\ifc{\Varid{e}}\mid \ifc{\Varid{v}}\;\otimes\;\ifc{E}\mid \mathbf{setLabel}\;\ifc{E}\mid \mathbf{sandbox}\;\ifc{E}{}\<[E]%
\\
\>[6]{}\hsindent{2}{}\<[8]%
\>[8]{}\mid {}\<[8E]%
\>[11]{}\mathbf{send}\;\ifc{E}\;\ifc{\Varid{e}}\;\ifc{\Varid{e}}\mid \mathbf{send}\;\ifc{\Varid{v}}\;\ifc{E}\;\ifc{\Varid{e}}\mid \mathbf{send}\;\ifc{\Varid{v}}\;\ifc{\Varid{v}}\;\ifc{E}{}\<[E]%
\\
\>[B]{}\ifc{\theta}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}(\ifc{l},\ifc{\Varid{i}}\;\ifc{\Varid{e}}){}\<[E]%
\\
\>[B]{}\ifc{\Theta}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\epsilon\mid \ifc{\theta},\ifc{\Theta}{}\<[E]%
\\
\>[B]{}\ifc{\Sigma}{}\<[6]%
\>[6]{}\Coloneqq{}\<[6E]%
\>[11]{}\emptyset\mid \ifc{\Sigma}\left[\ifc{\Varid{i}}\mapsto{}\ifc{\Theta}\right]{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

@@

\inferrule[I-getTaskId]
{ }
{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\mathbf{taskId}\right]\rightarrow\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\ifc{\Varid{i}}\right]}}

\and
\inferrule[I-getLabel]
{ }
{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\mathbf{getLabel}\right]\rightarrow\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\ifc{l}\right]}}

\and
\inferrule[I-setLabel]
{ \ensuremath{\ifc{l}\;\flows{}\;\ifc{l}'} }
{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\mathbf{setLabel}\;\ifc{l}'\right]\rightarrow\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}'}\left[\langle\rangle\right]}}
%{|fresh (id')|}

\and
\inferrule[I-send]
{
\ensuremath{\ifc{l}\;\flows{}\;\ifc{l}'}\\
\ensuremath{\ifc{\Sigma}\;(\ifc{\Varid{i}}')\mathrel{=}\ifc{\Theta}}\\
\ensuremath{\ifc{\Sigma}'\mathrel{=}\ifc{\Sigma}\left[\ifc{\Varid{i}}'\mapsto{}(\ifc{l}',\ifc{\Varid{i}},\ifc{\Varid{v}}),\ifc{\Theta}\right]}
}
{\ensuremath{\mathcal{E}_{\ifc{\Sigma}}^{\ifc{\Varid{i}},\ifc{l}}\left[\mathbf{send}\;\ifc{\Varid{i}}'\;\ifc{l}'\;\ifc{\Varid{v}}\right]\rightarrow\mathcal{E}_{\ifc{\Sigma}'}^{\ifc{\Varid{i}},\ifc{l}}\left[\langle\rangle\right]}}
